A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-11 skeleton_and_pathtracing.tex
Renommage fichier tex application
Quelques corrections

\def\Nset{\mathbb{N}}
\def\Zset{\Z}
\def\Nset{\mathbb{N}}
\def\Rset{\mathbb{R}}
\def\Z{\mathbb{Z}}
\def\Zhalf{\frac{\mathbb{Z}}{2}}
\def\allfaces#1{\mathbb{F}^{#1}}
\def\subfaces#1#2{\allfaces{#1}_{#2}}
\def\subcomplex#1#2{#1 \preceq #2}
\def\complex#1#2{\subcomplex{#2}{\allfaces{#1}}}
\def\cell#1{\hat{#1}}
\def\cellstrict#1{\hat{#1}^*}
\def\cont#1{\check{#1}}
\def\contstrict#1{\check{#1}^*}
\def\closure#1{#1^-}
\def\princ#1{#1^+}
\def\detach#1#2{#2 \oslash #1}
\def\attach#1#2{\mbox{\it{}Attach\/}(\cell{#1},#2)}
\def\mydim#1{\dim(#1)}
\def\type#1{\mbox{\it{}Dir\/}(#1)}
\def\orient#1{\mbox{\it{}Orient\/}(#1)}
\def\border#1{\mbox{\it{}Border\/}(#1)}
\def\suchthat{\;|\;}
\def\inter{\cap}
\def\union{\cup}
\def\dinterval#1#2{\{#1,\ldots,#2\}}
\newcommand{\Compl}[1]{\overline{#1}}
\def\finproof{\square}
\def\Zhalf{\frac{\mathbb{Z}}{2}}
\newcommand{\Card}[1]{|#1|}

@@

To do so, we associate to each element of $S\subseteq \Zset^n$ an n-face of $\allfaces{n}$. More precisely, let $x=(x_1,...,x_n) \in S$, we define the n-face $\Phi(x) = \{x_1, x_1 + 1\} \times \ldots \times \{x_n, x_n + 1\}$. We can extend the map $\Phi$ to sets: $\Phi(S)=\{\Phi(x) | x \in S\}$. Given a set $S \subset \Zset^n$, we associate to it the cubical complex $\closure{\Phi(S)}$.

@@

\section{A parallel directional thinning based on cubical complex}
\label{sec::skeletonization}

@@

Different definitions of the orientation and direction can be given, corresponding to different order of removal of free faces in the complex and leading to different results.
Algorithm~\ref{algo::pardircollapse_v0} can be implemented to run in linear time complexity (proportionally to the number of faces of the complex). Indeed, checking if a face is free or not may be easily done in constant time. Moreover, when a free pair $(f,g)$ is removed from the input complex, it is sufficient to scan the elements of $(\cellstrict{f} \union \contstrict{g})$ in order to find new free faces.

\section{Aspect preservation during thinning: a parameter-free method}
\label{sec::aspect_no_param}
Algorithm \ref{algo::pardircollapse_v0} does not necessarily preserves "geometrical information" from the original object in the resulting skeleton. For example, if the input was a filled human shape (one connected component, no tunnel nor cavity) and that $W=\emptyset$ and $l=+\inf$, then the result of Alg.~\ref{algo::pardircollapse_v0} would be a simple vertex. However, when one wants to preserve "geometrical information" from the original shape in the skeleton, then one expects to obtain a "stickman" from a human shape. It is however important to not retain "too much information" during thinning in order to avoid noisy branches in the skeleton.

In the following, we will see a new method in the cubical complex, requiring no user input, for obtaining a curvilinear skeleton yielding satisfactory visual properties. This will be achieved by adding, in the set $W$ of Alg.~\ref{algo::pardircollapse_v0}, some faces from the original object during the thinning process.

@@

We set $\dist1(x,y)$ as the length of the shortest $1$-path from $x$ to $y$. Let $S \subset \Zset^n$, we set, for all $x \in Zset^n$, the map $\Dist1{S}: \Zset^n \rightarrow \Nset$ such that $\Dist1{S}(x) = \displaystyle \min_{y \in \Compl{S}} \dist1(x,y)$.

@@

In order to extend all these previous maps defined in $\Zset^n$ to the cubical complex framework, let us introduce the map $\Phi^{-1}$, inverse of the bijective map $\Phi : \subfaces{n}{n} \rightarrow \Zset^{n}$ defined in Sec.~\ref{sec::binary_to_cubic}. It is used to project any $n$-face of $\allfaces{n}$ into $\Zset^n$. We indifferently use $\Phi^{-1}$ as a map from $\subfaces{n}{n}$ to $\Zset^n$, and as a map from $\mathcal{P}(\subfaces{n}{n})$ to $\mathcal{P}(\Zset^n)$.

Given $Y \subset \allfaces{n}$, we define the map $\cplDist1{Y}: \allfaces{n} \rightarrow \Nset$ as follows: for all $f \in \allfaces{n}$,

\bigskip
\begin{math}
\cplDist1{Y}(f) = \left\{
\begin{array}{ll}
\Dist1{\Phi^{-1}(Y \inter \subfaces{n}{n})}(Phi^{-1}(f)) & \text{if $f$ is an $n$-face}\\
\displaystyle \max_{g \in \contstrict{f} \inter \subfaces{n}{n}} \cplDist1{Y}(g) & \text{else}
\end{array}
\right.
\end{math}

@@

\input{pathtracint_application_skeleton}

>>>>

\def\V2C{\Psi}
\def\Nset{\mathbb{N}}
\def\Zset{\Z}
\def\Nset{\mathbb{N}}
\def\Rset{\mathbb{R}}
\def\Z{\mathbb{Z}}
\def\Zhalf{\frac{\mathbb{Z}}{2}}
\def\allfaces#1{\mathbb{F}^{#1}}
\def\subfaces#1#2{\allfaces{#1}_{#2}}
\def\subcomplex#1#2{#1 \preceq #2}
\def\complex#1#2{\subcomplex{#2}{\allfaces{#1}}}
\def\cell#1{\hat{#1}}
\def\cellstrict#1{\hat{#1}^*}
\def\cont#1{\check{#1}}
\def\contstrict#1{\check{#1}^*}
\def\closure#1{#1^-}
\def\princ#1{#1^+}
\def\detach#1#2{#2 \oslash #1}
\def\attach#1#2{\mbox{\it{}Attach\/}(\cell{#1},#2)}
\def\mydim#1{\dim(#1)}
\def\type#1{\mbox{\it{}Dir\/}(#1)}
\def\orient#1{\mbox{\it{}Orient\/}(#1)}
\def\border#1{\mbox{\it{}Border\/}(#1)}
\def\suchthat{\;|\;}
\def\inter{\cap}
\def\union{\cup}
\def\dinterval#1#2{\{#1,\ldots,#2\}}
\newcommand{\Compl}[1]{\overline{#1}}
\def\finproof{\square}
\def\Zhalf{\frac{\mathbb{Z}}{2}}
\newcommand{\Card}[1]{|#1|}

@@

To do so, we associate to each element of $S\subseteq \Zset^n$ an n-face of $\allfaces{n}$. More precisely, let $x=(x_1,...,x_n) \in S$, we define the n-face $\V2C(x) = \{x_1, x_1 + 1\} \times \ldots \times \{x_n, x_n + 1\}$. We can extend the map $\V2C$ to sets: $\V2C(S)=\{\V2C(x) | x \in S\}$. Given a set $S \subset \Zset^n$, we associate to it the cubical complex $\closure{\V2C(S)}$.

@@

\section{A parallel directional thinning based on cubical complex}

@@

Different definitions of the orientation and direction can be given, corresponding to different order of removal of free faces in the complex and leading to different results.
Algorithm~\ref{algo::pardircollapse_v0} can be implemented to run in linear time complexity (proportionally to the number of faces of the complex). Indeed, checking if a face is free or not may be easily done in constant time. Moreover, when a free pair $(f,g)$ is removed from the input complex, it is sufficient to scan the elements of $\cellstrict{f}$ in order to find new free faces.

\section{Aspect preservation during thinning: a parameter-free method}
\label{sec::aspect_no_param}
As previously said, our goal is to use the skeleton of a scene in order to guide light rays from the camera of the scene towards the light. In order to achieve this objective, we need a skeleton which \quotes{looks like} the original scene it was calculated from.

For example, if the input is a corridor (the void of the corridor), then the skeleton should be a line following the main direction of the corridor. 
However, Alg.~\ref{algo::pardircollapse_v0} does not necessarily preserve "geometrical features" of the input object in the resulting skeleton, which end up being a single vertex.
Moreover, when one wants to preserve "geometrical information" from the original shape in the skeleton, then it is important to not retain "too much information" during thinning in order to avoid noisy branches in the skeleton.

In the following, we give a new method requiring no user input, for obtaining a curvilinear skeleton yielding satisfactory visual properties. This will be achieved by adding, in the set $W$ of Alg.~\ref{algo::pardircollapse_v0}, some faces from the original object during the thinning process.

@@

We set $\dist1(x,y)$ as the length of the shortest $1$-path from $x$ to $y$. Let $S \subset \Zset^n$, we set, for all $x \in \Zset^n$, the map $\Dist1{S}: \Zset^n \rightarrow \Nset$ such that $\Dist1{S}(x) = \displaystyle \min_{y \in \Compl{S}} \dist1(x,y)$.

@@

In order to extend all these previous maps defined in $\Zset^n$ to the cubical complex framework, let us introduce the map $\V2C^{-1}$, inverse of the bijective map $\V2C : \Zset^{n} \rightarrow \subfaces{n}{n}$ defined in Sec.~\ref{sec::binary_to_cubic}. It is used to project any $n$-face of $\allfaces{n}$ into $\Zset^n$. We indifferently use $\V2C^{-1}$ as a map from $\subfaces{n}{n}$ to $\Zset^n$, and as a map from $\mathcal{P}(\subfaces{n}{n})$ to $\mathcal{P}(\Zset^n)$.

Given $Y \subset \allfaces{n}$, we set $S = \V2C^{-1}(Y \inter \subfaces{n}{n})$. We define the map $\cplDist1{Y}: \allfaces{n} \rightarrow \Nset$ as follows: for all $f \in \allfaces{n}$,

\bigskip
\begin{math}
\cplDist1{Y}(f) = \left\{
\begin{array}{ll}
\Dist1{S}(\V2C^{-1}(f)) & \text{if $f$ is an $n$-face}\\
\displaystyle \max_{g \in \contstrict{f} \inter \subfaces{n}{n}} \cplDist1{Y}(g) & \text{else}
\end{array}
\right.
\end{math}

@@

\input{application_to_path_tracing}
